---
title: "EY39 Data Analysis"
author: "Emily Yang"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(dplyr)
library(readxl)
df <- read_excel('EY39Data.xlsx')


```

```{r A1}

p <- ggplot(data=df)+ 
  geom_line(aes(Hours, A1, group=ID, colour=ID),
                data = . %>% filter(ID %in% c("Default" , "mCherry", "Alexa594")))
p <- p +labs(title="A1",
        x ="Time (hours)", y = "Fluorescence (AU)")
p
#ggsave("A1.png")

```
#####serrato

dummy <- df$A3

p <- ggplot(data=df)+ 
  geom_line(aes(Hours, dummy, group=ID, colour=ID),
                data = . %>% filter(ID %in% c("Default" , "mCherry", "Alexa594")))
p <- p +labs(title="dummy",
        x ="Time (hours)", y = "Fluorescence (AU)")
p

```{r A3}

p <- ggplot(data=df)+ 
  geom_line(aes(Hours, A3, group=ID, colour=ID),
                data = . %>% filter(ID %in% c("Default" , "mCherry", "Alexa594")))
p <- p +labs(title="A3",
        x ="Time (hours)", y = "Fluorescence (AU)")
p
#ggsave("A3.png")


```

```{r A5}

p <- ggplot(data=df)+ 
  geom_line(aes(Hours, A5, group=ID, colour=ID),
                data = . %>% filter(ID %in% c("Default" , "mCherry", "Alexa594")))
p <- p +labs(title="A5",
        x ="Time (hours)", y = "Fluorescence (AU)")
p
#ggsave("A5.png")

```


```{r A7}

p <- ggplot(data=df)+ 
  geom_line(aes(Hours, A7, group=ID, colour=ID),
                data = . %>% filter(ID %in% c("Default" , "mCherry", "Alexa594")))
p <- p +labs(title="A7",
        x ="Time (hours)", y = "Fluorescence (AU)")
p
#ggsave("A7.png")


```
```{r A9}

p <- ggplot(data=df)+ 
  geom_line(aes(Hours, A9, group=ID, colour=ID),
                data = . %>% filter(ID %in% c("Default" , "mCherry", "Alexa594")))
p <- p +labs(title="A9",
        x ="Time (hours)", y = "Fluorescence (AU)")
p
#ggsave("A9.png")


```

```{r C1}

p <- ggplot(data=df)+ 
  geom_line(aes(Hours, C1, group=ID, colour=ID),
                data = . %>% filter(ID %in% c("Default" , "mCherry", "Alexa594")))
p <- p +labs(title="C1",
        x ="Time (hours)", y = "Fluorescence (AU)")
p
#ggsave("C1.png")


```

```{r C3}

p <- ggplot(data=df)+ 
  geom_line(aes(Hours, C3, group=ID, colour=ID),
                data = . %>% filter(ID %in% c("Default" , "mCherry", "Alexa594")))
p <- p +labs(title="C3",
        x ="Time (hours)", y = "Fluorescence (AU)")
p
#ggsave("C3.png")
```
```{r C5}

p <- ggplot(data=df)+ 
  geom_line(aes(Hours, C5, group=ID, colour=ID),
                data = . %>% filter(ID %in% c("Default" , "mCherry", "Alexa594")))
p <- p +labs(title="C5",
        x ="Time (hours)", y = "Fluorescence (AU)")
p
#ggsave("C5.png")

```

```{r C7}

p <- ggplot(data=df)+ 
  geom_line(aes(Hours, C7, group=ID, colour=ID),
                data = . %>% filter(ID %in% c("Default" , "mCherry", "Alexa594")))
p <- p +labs(title="C7",
        x ="Time (hours)", y = "Fluorescence (AU)")
p
#ggsave("C7.png")
```
```{r C9}

p <- ggplot(data=df)+ 
  geom_line(aes(Hours, C9, group=ID, colour=ID),
                data = . %>% filter(ID %in% c("Default" , "mCherry", "Alexa594")))
p <- p +labs(title="C9",
        x ="Time (hours)", y = "Fluorescence (AU)")
p
#ggsave("C9.png")
```

```{r E1}

p <- ggplot(data=df)+ 
  geom_line(aes(Hours, E1, group=ID, colour=ID),
                data = . %>% filter(ID %in% c("Default" , "mCherry", "Alexa594")))
p <- p +labs(title="E1",
        x ="Time (hours)", y = "Fluorescence (AU)")
p
#ggsave("E1.png")

```

```{r E3}

p <- ggplot(data=df)+ 
  geom_line(aes(Hours, E3, group=ID, colour=ID),
                data = . %>% filter(ID %in% c("Default" , "mCherry", "Alexa594")))
p <- p +labs(title="E3",
        x ="Time (hours)", y = "Fluorescence (AU)")
p
#ggsave("E3.png")


```

```{r E5}

p <- ggplot(data=df)+ 
  geom_line(aes(Hours, E5, group=ID, colour=ID),
                data = . %>% filter(ID %in% c("Default" , "mCherry", "Alexa594")))
p <- p +labs(title="E5",
        x ="Time (hours)", y = "Fluorescence (AU)")
p
#ggsave("E5.png")


```

```{r E7}

p <- ggplot(data=df)+ 
  geom_line(aes(Hours, E7, group=ID, colour=ID),
                data = . %>% filter(ID %in% c("Default" , "mCherry", "Alexa594")))
p <- p +labs(title="E7",
        x ="Time (hours)", y = "Fluorescence (AU)")
p
#ggsave("E7.png")

```
```{r E9}

p <- ggplot(data=df)+ 
  geom_line(aes(Hours, E9, group=ID, colour=ID),
                data = . %>% filter(ID %in% c("Default" , "mCherry", "Alexa594")))
p <- p +labs(title="E9",
        x ="Time (hours)", y = "Fluorescence (AU)")
p
#ggsave("E9.png")

```

```{r G1}

p <- ggplot(data=df)+ 
  geom_line(aes(Hours, G1, group=ID, colour=ID),
                data = . %>% filter(ID %in% c("Default" , "mCherry", "Alexa594")))
p <- p +labs(title="G1",
        x ="Time (hours)", y = "Fluorescence (AU)")
p
#ggsave("G1.png")

```

```{r G3}

p <- ggplot(data=df)+ 
  geom_line(aes(Hours, G3, group=ID, colour=ID),
                data = . %>% filter(ID %in% c("Default" , "mCherry", "Alexa594")))
p <- p +labs(title="G3",
        x ="Time (hours)", y = "Fluorescence (AU)")
p
#ggsave("G3.png")


```

```{r G5}

p <- ggplot(data=df)+ 
  geom_line(aes(Hours, G5, group=ID, colour=ID),
                data = . %>% filter(ID %in% c("Default" , "mCherry", "Alexa594")))
p <- p +labs(title="G5",
        x ="Time (hours)", y = "Fluorescence (AU)")
p
#ggsave("G5.png")

```

```{r G7}

p <- ggplot(data=df)+ 
  geom_line(aes(Hours, G7, group=ID, colour=ID),
                data = . %>% filter(ID %in% c("Default" , "mCherry", "Alexa594")))
p <- p +labs(title="G7",
        x ="Time (hours)", y = "Fluorescence (AU)")
p
#ggsave("G7.png")

```

```{r Blank1}

p <- ggplot(data=df)+ 
  geom_line(aes(Hours, Blank1, group=ID, colour=ID),
                data = . %>% filter(ID %in% c("Default" , "mCherry", "Alexa594")))
p <- p +labs(title="Blank1",
        x ="Time (hours)", y = "Fluorescence (AU)")
p
#ggsave("Blank1.png")

```

```{r Blank2}

p <- ggplot(data=df)+ 
  geom_line(aes(Hours, Blank2, group=ID, colour=ID),
                data = . %>% filter(ID %in% c("Default" , "mCherry", "Alexa594")))
p <- p +labs(title="Blank2",
        x ="Time (hours)", y = "Fluorescence (AU)")
p
#ggsave("Blank2.png")
```

```{r Blank3}

p <- ggplot(data=df)+ 
  geom_line(aes(Hours, Blank3, group=ID, colour=ID),
                data = . %>% filter(ID %in% c("Default" , "mCherry", "Alexa594")))
p <- p +labs(title="Blank3",
        x ="Time (hours)", y = "Fluorescence (AU)")
p
#ggsave("Blank3.png")

``` 
